Interested in joining the team

### 2025-01-21 join.qmd
add summer award opportunities

General inquiries regarding undergraduate opportunities in the lab can be sent to cartem11 [at] mcmaster [dot] ca.

>>>>

General inquiries regarding other undergraduate opportunities in the lab such as NSERC USRA, Kinesiology Summer Research Award, MIRA Summer Research Fellowship, etc can be sent to cartem11 [at] mcmaster [dot] ca.
